>

### 2019-04-22 paper/spinifex-paper.tex
capitalised figure

In figure \ref{fig:step0} the contributions of the variables tars1 and
aede2 are mostly orthogonal to the contributions of the other four
variables. These two variables explain the variation of the data
distinguishing the purple cluster from the rest of the sample. Select
aede2 as the manip var, the variable to be manipulated, as it has a
larger contribution to the projection. The question that will be
explored is how important the variable aede2 is to the separation of the
clusters.

@@

We'll start by initializing values including a standardized data set
(numeric columns only), a starting basis, a categorical variable for
point aesthetics (optional), and a manip var. To get bearings on the
projection, start by observing the reference axes of the basis with
\texttt{view\_basis()} producing figure \ref{fig:step0}.

@@

After becoming familiar with this space, select a manip var, the
variable to change the contributions of. Use
\texttt{view\_manip\_space()} to view the new space with a dimension
orthogonal to the projection plane where the manip var has a full
contribution. This illustrates how the manip var is manipulated with the
addition of the manipulation space as shown in figure \ref{fig:step2}.

@@

Now we are ready to perform a manual tour on the selected variable. Use
\texttt{play\_manual\_tour()} to perform the algorithm as discussed
above, in section \ref{sec:algorithm}. This is the animated equivalent
of figure \ref{fig:step3}.

@@

The jet cluster resides in a smaller dimensionality than the full set of
experiments with four principal components explaining 95\% of the
variation in the cluster (Cook, Laa, and Valencia
\protect\hyperlink{ref-cook_dynamical_2018}{2018}). The data within this
4D embedding is subset down to ATLAS7old and ATLAS7new to focus in on
two groups with a reasonable number of observations that occupy
different parts of the subspace. Radial manual tours controlling
contributions from PC4 and PC3 are shown in figure
\ref{fig:JetClusterGood} and figure \ref{fig:JetClusterBad}
respectively. These variables are selected to contrast the difference of
information conveyed by touring different variables. Links to dynamic
HTML5 animations controlling each of the four variables are also
provided.

@@

A different space is used to explore the DIS cluster; specifically the
first six principal components, which explains 48\% of the variation
contained within the aggregated data (Cook, Laa, and Valencia
\protect\hyperlink{ref-cook_dynamical_2018}{2018}). Radial manual tours
are performed on PC6 and PC2 in figure \ref{fig:DISclusterGood} and
figure \ref{fig:DISclusterBad} respectively.

>>>>

In Figure \ref{fig:step0} the contributions of the variables tars1 and
aede2 are mostly orthogonal to the contributions of the other four
variables. These two variables explain the variation of the data
distinguishing the purple cluster from the rest of the sample. Select
aede2 as the manip var, the variable to be manipulated, as it has a
larger contribution to the projection. The question that will be
explored is how important the variable aede2 is to the separation of the
clusters.

@@

We'll start by initializing values including a standardized data set
(numeric columns only), a starting basis, a categorical variable for
point aesthetics (optional), and a manip var. To get bearings on the
projection, start by observing the reference axes of the basis with
\texttt{view\_basis()} producing Figure \ref{fig:step0}.

@@

After becoming familiar with this space, select a manip var, the
variable to change the contributions of. Use
\texttt{view\_manip\_space()} to view the new space with a dimension
orthogonal to the projection plane where the manip var has a full
contribution. This illustrates how the manip var is manipulated with the
addition of the manipulation space as shown in Figure \ref{fig:step2}.

@@

Now we are ready to perform a manual tour on the selected variable. Use
\texttt{play\_manual\_tour()} to perform the algorithm as discussed
above, in section \ref{sec:algorithm}. This is the animated equivalent
of Figure \ref{fig:step3}.

@@

The jet cluster resides in a smaller dimensionality than the full set of
experiments with four principal components explaining 95\% of the
variation in the cluster (Cook, Laa, and Valencia
\protect\hyperlink{ref-cook_dynamical_2018}{2018}). The data within this
4D embedding is subset down to ATLAS7old and ATLAS7new to focus in on
two groups with a reasonable number of observations that occupy
different parts of the subspace. Radial manual tours controlling
contributions from PC4 and PC3 are shown in Figure
\ref{fig:JetClusterGood} and Figure \ref{fig:JetClusterBad}
respectively. These variables are selected to contrast the difference of
information conveyed by touring different variables. Links to dynamic
HTML5 animations controlling each of the four variables are also
provided.

@@

A different space is used to explore the DIS cluster; specifically the
first six principal components, which explains 48\% of the variation
contained within the aggregated data (Cook, Laa, and Valencia
\protect\hyperlink{ref-cook_dynamical_2018}{2018}). Radial manual tours
are performed on PC6 and PC2 in Figure \ref{fig:DISclusterGood} and
Figure \ref{fig:DISclusterBad} respectively.

### 2019-04-22 paper/spinifex_paper.Rmd
capitalised figure

<!-- select a manip var-->
In figure \ref{fig:step0} the contributions of the variables tars1 and aede2 are mostly orthogonal to the contributions of the other four variables. These two variables explain the variation of the data distinguishing the purple cluster from the rest of the sample. Select aede2 as the manip var, the variable to be manipulated, as it has a larger contribution to the projection. The question that will be explored is how important the variable aede2 is to the separation of the clusters.

@@

We'll start by initializing values including a standardized data set (numeric columns only), a starting basis, a categorical variable for point aesthetics (optional), and a manip var. To get bearings on the projection, start by observing the reference axes of the basis with `view_basis()` producing figure \ref{fig:step0}.

@@

After becoming familiar with this space, select a manip var, the variable to change the contributions of. Use `view_manip_space()` to view the new space with a dimension orthogonal to the projection plane where the manip var has a full contribution. This illustrates how the manip var is manipulated with the addition of the manipulation space as shown in figure \ref{fig:step2}.

@@

Now we are ready to perform a manual tour on the selected variable. Use `play_manual_tour()` to perform the algorithm as discussed above, in section  \ref{sec:algorithm}. This is the animated equivalent of figure \ref{fig:step3}.

@@

<!-- jet cluster, explain dimensionality -->
The jet cluster resides in a smaller dimensionality than the full set of experiments with four principal components explaining 95% of the variation in the cluster [@cook_dynamical_2018]. The data within this 4D embedding is subset down to ATLAS7old and ATLAS7new to focus in on two groups with a reasonable number of observations that occupy different parts of the subspace. Radial manual tours controlling contributions from PC4 and PC3 are shown in figure \ref{fig:JetClusterGood} and figure \ref{fig:JetClusterBad} respectively. These variables are selected to contrast the difference of information conveyed by touring different variables. Links to dynamic HTML5 animations controlling each of the four variables are also provided.

@@

<!-- introduce DIS cluster -->
A different space is used to explore the DIS cluster; specifically the first six principal components, which explains 48% of the variation contained within the aggregated data [@cook_dynamical_2018]. Radial manual tours are performed on PC6 and PC2 in figure \ref{fig:DISclusterGood} and figure \ref{fig:DISclusterBad} respectively.

>>>>

<!-- select a manip var-->
In Figure \ref{fig:step0} the contributions of the variables tars1 and aede2 are mostly orthogonal to the contributions of the other four variables. These two variables explain the variation of the data distinguishing the purple cluster from the rest of the sample. Select aede2 as the manip var, the variable to be manipulated, as it has a larger contribution to the projection. The question that will be explored is how important the variable aede2 is to the separation of the clusters.

@@

We'll start by initializing values including a standardized data set (numeric columns only), a starting basis, a categorical variable for point aesthetics (optional), and a manip var. To get bearings on the projection, start by observing the reference axes of the basis with `view_basis()` producing Figure \ref{fig:step0}.

@@

After becoming familiar with this space, select a manip var, the variable to change the contributions of. Use `view_manip_space()` to view the new space with a dimension orthogonal to the projection plane where the manip var has a full contribution. This illustrates how the manip var is manipulated with the addition of the manipulation space as shown in Figure \ref{fig:step2}.

@@

Now we are ready to perform a manual tour on the selected variable. Use `play_manual_tour()` to perform the algorithm as discussed above, in section  \ref{sec:algorithm}. This is the animated equivalent of Figure \ref{fig:step3}.

@@

<!-- jet cluster, explain dimensionality -->
The jet cluster resides in a smaller dimensionality than the full set of experiments with four principal components explaining 95% of the variation in the cluster [@cook_dynamical_2018]. The data within this 4D embedding is subset down to ATLAS7old and ATLAS7new to focus in on two groups with a reasonable number of observations that occupy different parts of the subspace. Radial manual tours controlling contributions from PC4 and PC3 are shown in Figure \ref{fig:JetClusterGood} and Figure \ref{fig:JetClusterBad} respectively. These variables are selected to contrast the difference of information conveyed by touring different variables. Links to dynamic HTML5 animations controlling each of the four variables are also provided.

@@

<!-- introduce DIS cluster -->
A different space is used to explore the DIS cluster; specifically the first six principal components, which explains 48% of the variation contained within the aggregated data [@cook_dynamical_2018]. Radial manual tours are performed on PC6 and PC2 in Figure \ref{fig:DISclusterGood} and Figure \ref{fig:DISclusterBad} respectively.
